---
title: 'Replication #2'
author: "Jack Schroeder"
date: "2/18/2019"
output:
  pdf_document: default
  html_document: default
citation_package: natbib
bibliography: bibliography.bib
---

## Abstract

I replicate "Causal effect of intergroup contact on exclusionary attitudes" (@enos2014) using code/data deposited in the Harvard Dataverse (@DVN/DOP4UB_2017). There are two figures and three tables in the original article. Figure 2 and Tables 1 and 2 can be, almost, perfectly replicated. Table 3 and Figure 1 can not be replicated from the code/data on deposit at the Dataverse.  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Begin by calling for Enos' libraries.

library(stargazer)
library(tidyverse)
library(ri)
library(RItools)

# Enos had this in to set scientific notation.

options(scipen = 999)  

# This code will load in the data for the paper.

dat.all <- read.csv('Enos Code/pnas_data.csv')
dat.t1 <- read.csv('Enos Code/t1_data.csv')
dat.all.prime <- read.csv('Enos Code/prime_data.csv')

```

```{r, echo=FALSE}
# I like the idea of using logistic regression to analyze Enos' results.
# To do so, I need to add a column to dat.all that equals 1 if the 
# respondent became more conservative and a 0 if there was no change or
# if the respondent became more liberal. I think coding no change as a 0
# rather than a 1 will make any statistically significant results more
# robust and help avoid a Type I error.

dat.all <- dat.all %>% 
  mutate(Remain.b = case_when((Remain.y-Remain.x) > 0 ~ 1,
                              TRUE ~ 0),
         numberim.b = case_when((numberim.y - numberim.x) > 0 ~ 1,
                                TRUE ~ 0),
         Englishlan.b = case_when((Englishlan.y - Englishlan.x) > 0 ~ 1,
                                  TRUE ~ 0),
         Overall.b = case_when((Remain.y + numberim.y + Englishlan.y) - (Remain.x + numberim.x + Englishlan.x) > 0 ~ 1,
                               TRUE ~ 0))
```

```{r main results, echo=FALSE}

# This code chunk is here to create Table 1. The first 
# thing Enos does is create the vectors for each question
# that was asked. He also assigns x.names, y.names, and 
# covariates, but I am not sure what their purposes are.

repeats <- c("numberim","Remain","Englishlan")
x.names <- paste(repeats,".x",sep="")
y.names <- paste(repeats,".y",sep="")
b.names <- paste(repeats,".b",sep="")
covariates <- c('line.x')


# Enos makes the matrix that will include the final results.

final.mat <- matrix(nrow = 0, ncol = 10)

# These vectors will subset the data by waiting preference.

subsets <- c('all','no.car')

# The for loop here is taking the subsets created above
# (all and no.car) and creating the conditions to make
# Table 1.

for(subset in subsets){

	out.mat = matrix(nrow = length(repeats), ncol = 10)
	
# Looking at all respondents.
	
	if(subset == 'all'){
		dat.subset = dat.all
	}
	
# Essentially filtering out respondents who wait in their
# cars (we want people waiting on a platform to hear the
# confederates speak Spanish).
	
	if(subset ==  'no.car'){
		dat.subset = dat.all[dat.all$habits != 1,]
		}

# I am not sure what a z-variable is here.
	
	z.variable = 'treatment'

# Another for loop within this for loop. This one looks at
# repeats, which was created above, and subsets the data
# accordingly. This is to distinguish by question. Then
# the loop presumably looks at the Average Treatment
# Effects, along with the Conditional Average Treatment
# Effects of each question.
	
	for(j in 1:length(repeats)){
		dat.subset$x.new = (as.numeric(dat.subset[,x.names[j]])-1)/4  

# The -1 and /4 rescale x to 0-1. The same is done for y. Why is
# this done? The responses to the three questions were given on
# a five-point scale, which when one is subtracted and then 
# the result is divided by 4, yields a scaled answer.
		
		dat.subset$y.new = (as.numeric(dat.subset[,y.names[j]])-1)/4
		
# I found it easier to just modify Enos' original for loop and add
# the new binary into the mix.
		
		dat.subset$b.new = as.numeric(dat.subset[,b.names[j]])
		dat.subset$Y = dat.subset$y.new - dat.subset$x.new
		
		dat.use = dat.subset[is.na(dat.subset$Y) == F,]

# The means and standard deviations of x.new and y.new are found
# (disregarding NA values, of course).
		
		x.sd = sd(dat.use$x.new,na.rm = T)
		x.mean = mean(dat.use$x.new,na.rm = T)
		y.mean = mean(dat.use$y.new,na.rm = T)
		b.sd = sd(dat.use$b.new, na.rm=T)
		b.mean = mean(dat.use$b.new, na.rm = T)

# Not entirely sure what this line does.
		
		y.treat = mean(dat.use$y.new[dat.use$treatment==1],na.rm = T)

# Enos then creates the tables that will be used to help
# create Table 1. It is a treatment table that focuses on stations
# since some stations were control and others were treatment.
		
		station.treatment.table = table(dat.use$station,dat.use[,z.variable])
		no.control.stations = names(which(station.treatment.table[,1] == 0))
		no.treatment.stations = names(which(station.treatment.table[,2] == 0))
		dat.use = dat.use[!dat.use$station%in%c(no.control.stations,no.treatment.stations),]
				
# Assuming that making each station a factor makes the vector 
# easier to work with.
		
		dat.use$station = factor(dat.use$station)
		dat.use$treated_unit = factor(dat.use$treated_unit)
		Xs = data.matrix(dat.use[,covariates])
		
		perms <- genperms(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		probs = genprobexact(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)

# Enos finds the Average Treatment Effects here. I'm not really
# sure how this is done (what is estate?). Would love to learn
# more about this in class.
		
		ate = estate(Y = dat.use$Y, Z = dat.use[,z.variable], X = Xs, prob = probs)
		Ys = genouts(Y = dat.use$Y, Z = dat.use[,z.variable], ate = 0)

# Is gendist gender? Distance?

		distout <- gendist(Ys,perms, prob=probs)
		disp =	dispdist(distout, ate = ate, display.plot = F)

# Also unfamiliar with the usage of j.
		
		out.mat[j,1] = repeats[j]
		out.mat[j,2] = subset
		out.mat[j,3] = nrow(dat.use)
		out.mat[j,4] = ate
		out.mat[j,5] = disp$greater.p.value
		out.mat[j,6] = disp$lesser.p.value
		out.mat[j,7] = x.sd
		out.mat[j,8] = x.mean
		out.mat[j,9] = b.sd
		out.mat[j,10] = b.mean
	}
	
# Enos just binds together the two matrices.
	
	final.mat = rbind(final.mat,out.mat)
}

# And makes them into a data frame, to which he adds
# column names.

final.mat <- as.data.frame(final.mat)
colnames(final.mat) <- c('variable','subset','N','ate','greater.p.value','lesser.p.value','x.sd','x.mean', 'b.sd', 'b.mean')

# He reassigns this data frame for later use.

final.mat.main <- final.mat
```

```{r, echo=FALSE}
# Preceptor's code from last week inspires me to change these factors into numerics.

final.mat.main$ate    <- as.numeric(as.character(final.mat.main$ate)) 
final.mat.main$N      <- as.numeric(as.character(final.mat.main$N)) 
final.mat.main$x.mean <- as.numeric(as.character(final.mat.main$x.mean)) 
final.mat.main$x.sd   <- as.numeric(as.character(final.mat.main$x.sd)) 
final.mat.main$greater.p.value <- as.numeric(as.character(final.mat.main$greater.p.value)) 
final.mat.main$b.sd <- as.numeric(as.character(final.mat.main$b.sd))
final.mat.main$b.mean <- as.numeric(as.character(final.mat.main$b.mean))

remain_1 <- glm(Remain.b ~ treatment, data = dat.all, family=binomial)

remain_2 <- glm(Remain.b ~ treatment + male, data = dat.all, family=binomial)

remain_3 <- glm(Remain.b ~ treatment + age, data = dat.all, family=binomial)

numberim_1 <- glm(numberim.b ~ treatment, data = dat.all, family=binomial)

Englishlan_1 <- glm(Englishlan.b ~ treatment + male + age, data = dat.all, family=binomial)

Overall_1 <- glm(Overall.b ~ treatment, data = dat.all, family=binomial)


```

```{r, results = "asis"}
stargazer(remain_1, remain_2, remain_3,
          header = TRUE,
          style = "ajps",
          dep.var.labels = "Children of uncodumented be allowed to stay?",
          omit.stat = c("f","ser","aic","LL"),
          covariate.labels = c("Treatment", "Male", "Age"),
          digits = 2)
```


## References